Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-04 Experiments.tex
minor fixes to language, space saving etc.
refinements  - wordsmithing and shortening.

Comments to address in this section:
\begin{enumerate}
    \item REVIEWER 2: In the weak scalability evaluations (in Figure 7 and
    8), the overhead of the Next Generation Executor (NGE) has grown linearly
    with the number of the nodes. Can you explain why the average time
    execution time of AthenaMP is decreased even when the overhead is
    increasing?
    I checked the data. Figure 8 was simply wrong. I think that we have overwritten the original with an older version.  Figure 7: I used a smaller integration step to compute the integral of the pilot concurrency. It gets better but not as much as I would like. Our data has something sketchy.  
\end{enumerate}

@@

Tasks do not wait within the NGE Agent's queue since one node is available to
each AthenaMP instance. Overheads in task execution are consequence primarily
of the three other factors: (i) the initial bootstrapping of the pilot on the
nodes; (ii) the UnitManager's dispatching of units (tasks) to the agent; and
(iii) time for the agent to bootstrap all the tasks on the nodes.

@@

In these experiments, we run five AthenaMP instances per node. As these
experiments are designed to investigate the overhead generated by the
scheduling and bootstrap of AthenaMP instances, we reduced the number of
events simulated by each AthenaMP task to sixteen in such a way that the
running time of each AthenaMP is, on average, $\sim 1200$ seconds. This
experiment design choice does not affect the objectives or accuracy of the
experiments, but allows us to scale experiments to large node counts by being
conservative with allocation.

>>>>

\ifreview
Comments to address in this section:
\begin{enumerate}
    \item REVIEWER 2: In the weak scalability evaluations (in Figure 7 and
    8), the overhead of the Next Generation Executor (NGE) has grown linearly
    with the number of the nodes. Can you explain why the average time
    execution time of AthenaMP is decreased even when the overhead is
    increasing?
    I checked the data. Figure 8 was simply wrong. I think that we have overwritten the original with an older version.  Figure 7: I used a smaller integration step to compute the integral of the pilot concurrency. It gets better but not as much as I would like. Our data has something sketchy.  
\end{enumerate}
\fi

@@

Tasks do not wait within the NGE Agent's queue since one node is available to
each AthenaMP instance. Task execution  overheads result primarily from  three
factors: (i) the initial bootstrapping of the pilot on the nodes; (ii) the
UnitManager's dispatching of units (tasks) to the agent; and (iii) time for
the agent to bootstrap all the tasks on the nodes.

@@

In these experiments, we run five AthenaMP instances per node. As these
experiments are designed to investigate the overhead of 
scheduling and bootstraping of AthenaMP instances, the number of
events simulated by each AthenaMP task was reduced to sixteen such that the
running time of each AthenaMP was, on average, $\sim 1200$ seconds. This
experiment design choice does not affect the objectives or accuracy of the
experiments, but allows us to scale experiments to large node counts by being
conservative with allocation.

### 2017-07-04 bckground.tex
refinements  - wordsmithing and shortening.

AliEn, DIRAC, GlideinWMS and PanDA also have similar implementations. These WMS
were initially implemented to use Grid resources, using one or more components
to the Condor software ecosystem~\cite{thain2005distributed} and, as with
GlideinWMS, contributing to its development. Accordingly, all LHC WMS
implemented Grid-like authentication and authorization systems and adopted a
computational model based on distributing a large amount of single/few-cores
tasks across hundreds of sites\mtnote{Is this true?}.

All the experiments at LHC produces and process large amount of data both from
actual collisions in the accelerator and from their simulations. Dedicated,
multi-tiered data systems have been built to store, replicate, and distributed
these data. All LHC WMS interface with these systems to move data to the sites
where related compute tasks are executed or to schedule compute tasks where
(large amount of) data are already stored.

>>>>

%~\cite{thain2005distributed}

AliEn, DIRAC, GlideinWMS and PanDA also have similar implementations. These
WMS were initially implemented to use Grid resources using the Condor software
ecosystem~\cite{thain2005distributed}. Accordingly, all LHC WMS implemented
Grid-like authentication and authorization systems and adopted a computational
model based on distributing a large amount of single/few-cores tasks across
hundreds of sites\mtnote{Is this true?}.

All LHC experiments produce and process large amounts  of data from actual
collisions in the accelerator and from their simulations. Dedicated, multi-
tiered data systems have been built to store, replicate, and distributed these
data. All LHC WMS interface with these systems to move data to the sites where
related compute tasks are executed or to schedule compute tasks where (large
amount of) data are already stored.
